Nyx interfaces with two post-processing suites, Reeber and Gimlet.

\section{Reeber}

Reeber uses topological methods to construct merge trees of scalar fields.
These trees are effectively parameter-independent and contain a complete
description of the field topology. In the context of Nyx, the field of interest
is the dark matter density. Nyx then queries the merge tree with user-defined
runtime parameters in order to locate the volume-averaged center of dark matter
halos. The same tree can be queried with any number of such parameters to find
halos with different mass/density thresholds.

\section{Gimlet}

Gimlet computes a variety of quantities about the simulation, including optical
depths, Lyman-alpha fluxes, power spectra (both 1-D ``line-of-sight'' as well as
fully 3-D), and probability distribution functions. These suites are fully
MPI-parallel and can be run either ``in situ'' or ``in-transit,'' or with a
combination of both. A detailed description of their usage is provided in the
Nyx User Guide.

\section{Usage}

Nyx can post-process with Gimlet alone, with Reeber alone, or with both
simultaneously. To compile with Gimlet, add \texttt{GIMLET = TRUE} to the
\texttt{GNUmakefile}; to compile with Reeber, add \texttt{REEBER = TRUE}. Note
that these codes are in separate repositories and are not included with Nyx.

Nyx and BoxLib provide the capability for the user to execute an arbitrary
post-processing workflow either \textit{in situ} or in-transit. An \textit{in
situ} workflow is one in which all MPI processes evolving the simulation stop
at specified time steps and perform the post-processing before continuing with
the simulation. In-transit means that BoxLib creates a disjoint group of MPI
processes (``sidecars'') from the global pool and reserves them exclusively for
post-processing. At specified time steps the group of processes evolving the
simulation will send the necessary data to the sidecar group, and then will
continue with the simulation. The two groups then work independently of one
another on their particular tasks.

To run the post-processing workflow \textit{in situ}, one sets the
\texttt{nSidecars} parameter in the inputs file to \texttt{0}. To run the
workflow in-transit, one sets \texttt{nSidecars > 0}. Note that the sum of all
MPI processes is constant for the duration of the simulation, so whatever
number the user dedicates to post-processing will be subtracted from the number
doing the simulation itself.
